Holomorphic field theories and higher algebra

### 2024-09-12 draft.tex
renorm

>>>>

The idea of renormalization is a necessary ingredient in producing examples of typical (Riemannian or Lorentzian) quantum field theories.
One can apply the same sort of techniques to produce holomorphic quantum field theories, and the higher algebraic structures associated to them.
A key feature of holomorphic theories is the absence of (possibly scheme-dependent) counterterms which can make typical quantum field theories difficult to access.

Counterterms are perturbative quantum effects that typically must be introduced to the action functional in order to circumvent ultra-violet (UV, high energy) divergences which arise when studying the path integral.
From Feynman, we know that the path integral can be formally expressed in terms of graphs. 
More precisely, given a graph $\Gamma$ (whose exact shape depends on the theory), there is a prescription for assigning to it a functional $W_\Gamma$ on the fields (a distribution) which we can understand as term in the quantum action; typically in the form of an integral over $|V(\Gamma)|$ copies of spacetime where $V(\Gamma)$ is the vertex set of the graph.
Unfortunately, this prescription is not always well-posed, as there are infinities which can arise due to presence of overlapping supports of certain distributions.
Counterterms can be constructed by carefully understanding the nature of these divergences through some regularization scheme.

For topological quantum field theories, it is known from the work of Axelrod, Singer, Kontsevich, Cattaneo, and others \cite{???} that such Feynman graphs return finite answers and hence there is no need to introduce such complications.
The method used to prove this interprets such Feynman graph integrals as integrals over configuration space and then showing that the weights $W_\Gamma$ can be extended to some compactification.
A different regularization scheme based on the heat equation was used by Costello \cite{CosRenormPaper} to arrive at the same result for topological quantum field theories.

The configuration space method traditionally used to study topological theories does not admit an immediate generalization to holomorphic theories.
Nevertheless, it is known that the renormalization for holomorphic field theories is equally well-behaved.

The heat kernel analysis of the perturbative renormalization for holomorphic quantum field theories was initiated by Costello and Li in their study of the $B$-model topological string field theory \cite{??}.
Later, in \cite{Whol} we have shown more broadly that holomorphic field theories in any dimension (on flat space) are UV finite to first-order in perturbation theory.
In \cite{LiVertex} it is shown by a very clever analysis that holomorphic field theories in complex dimension one (chiral conformal field theories) are finite to all orders in perturbation theory; this was later extended to arbitrary Riemann surfaces in \cite{Jie and Si}.
There has a been a buzz of recent activity contributing to the advancement in the renormalization of holomorphic field theories.
In work of Budzik, Gaiotto, Kulp, Wu, Yu, a strategy for proving UV finiteness for certain graphs (called Laman graphs) at arbitrary genus in a holomorphic quantum field theory is developed \cite{BGKWY}.
The key idea is to combine the heat kernel analysis with the sort of compactifications that are used in the theory of configuration spaces.
Following this work, Minghao Wang has extended this analysis to show that holomorphic field theories on $\C^n$ admit a regulation scheme which is UV finite to \textit{all} orders in perturbation theory \cite{Wang}.
In other words, both topological and holomorphic field theories are completely free of the divergences present in typical quantum field theories!

The discussion so far in this section was about the analytic issues which are present when trying to make the path integral precise.
For interesting quantum field theories, like gauge theories, there is another issue which could prevent the theory from being well-posed; these are called anomalies.
An anomaly is the measure of the failure of the quantum path integral to enjoy the same symmetries as the underlying classical field theory.
In gauge theory, for instance, there could be an obstruction for the perturbative renormalization to be gauge invariant.
In topological theories, it is known that these sort of anomalies are absent.
For holomorphic theories, however, anomalies are present.\footnote{Anomalies in holomorphic field theory are related to, but distinct from, familiar anomalies such as `chiral anomalies' in theories of Weyl fermions.}
Since renormalization is so well-behaved, however, such anomalies are amenable to explicit characterization.
For example, at one-loop in perturbation theory, an explicit formula for such anomalies for holomorphic theories on $\C^d$ is given in \cite{Whol}.
It involves a sum over Feynman weights $W_\Gamma$ where $\Gamma$ is a polygon with $(d+1)$-vertices.
